Preprocessing

### 2023-07-14 docs/presentation/preprocess.Rmd
viz: density plots

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
# library(showtext)
# font_add_google("Fira Sans", "Fira Sans")
```

@@

```{r q5}

```

>>>>

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
library(showtext)
font_add_google("Fira Sans", "Fira Sans")
```

@@

```{r q5}
four_levels = list(
  "To a great extent" = 1,
  "Somewhat" = 0.66,
  "Very little" = 0.33,
  "Not at all" = 0
)

analysis %>%
  mutate(Q5_num = as.numeric(four_levels[Q5])) %>%
  ggplot() +
  scale_x_continuous(
    breaks = as.numeric(four_levels),
    labels = str_wrap(names(four_levels), width = 9)
  ) +
  geom_density(aes(x = Q5_num), adjust = 1.6) +
  theme_minimal() +
  theme(
    text = element_text(family = "Fira Sans", size = 16),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  ) +
  labs(
    title = "How familiar are you with the term \"reproducibility\"?",
    subtitle = "In the context of conducting research",
    x = "", y = ""
  )
```
